\documentclass[11pt]{article}
\usepackage{amssymb,amsmath,amsthm,graphicx}
\usepackage{fancyhdr}

\def\shownotes{1}   % set 1 for version with author notes
                    % set 0 for no notes



%uncomment to get hyperlinks
%\usepackage{hyperref}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Some macros (you can ignore everything until "end of macros")

\topmargin 0pt \advance \topmargin by -\headheight \advance
\topmargin by -\headsep

\textheight 8.9in

\oddsidemargin 0pt \evensidemargin \oddsidemargin \marginparwidth
0.5in

\textwidth 6.5in

%%%%%%

\providecommand{\vs}{vs. }
\providecommand{\ie}{\emph{i.e.,} }
\providecommand{\eg}{\emph{e.g.,} }
\providecommand{\cf}{\emph{cf.,} }
\providecommand{\etc}{\emph{etc.} }

\newcommand{\getsr}{\gets_{\mbox{\tiny R}}}
\newcommand{\bits}{\{0,1\}}
\newcommand{\bit}{\{0,1\}}
\newcommand{\Ex}{\mathbb{E}}
\newcommand{\eqdef}{\stackrel{def}{=}}
\newcommand{\To}{\rightarrow}
\newcommand{\e}{\epsilon}
\newcommand{\R}{\mathbb{R}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Gen}{\mathsf{Gen}}
\newcommand{\Enc}{\mathsf{Enc}}
\newcommand{\Dec}{\mathsf{Dec}}
\newcommand{\Sign}{\mathsf{Sign}}
\newcommand{\Ver}{\mathsf{Ver}}

\providecommand{\mypara}[1]{\smallskip\noindent\emph{#1} }
\providecommand{\myparab}[1]{\smallskip\noindent\textbf{#1} }
\providecommand{\myparasc}[1]{\smallskip\noindent\textsc{#1} }
\providecommand{\para}{\smallskip\noindent}


\newtheorem{theorem}{Theorem}
\theoremstyle{definition}
\newtheorem{ex}{Exercise}
\newtheorem{definition}{Definition}

%%%%%%%  Author Notes %%%%%%%d
%
\ifnum\shownotes=1
\newcommand{\authnote}[2]{{ $\ll$\textsf{\footnotesize #1 notes: #2}$\gg$}}
\else
\newcommand{\authnote}[2]{}
\fi
\newcommand{\Snote}[1]{{\authnote{Solution}{#1}}}
\newcommand{\Inote}[1]{{\authnote{Solution}{#1}}}
\newcommand{\Ichanged}[1]{{\authnote{Changed}{#1}}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\VAR}{\mathrm{VAR}}



% end of macros
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


% page counting, header/footer
\usepackage{fancyhdr}
\pagestyle{fancy}
\lhead{\footnotesize \parbox{11cm}{CS350, Boston University, Fall 2015} }
\rhead{Erik Brakke}
\renewcommand{\headheight}{24pt}

\begin{document}

\title{Homework 7}
\author{Erik Brakke}
\maketitle

\thispagestyle{fancy}
 
 
\section*{Answer 1}
This code will work\\
The scenarios here are the either a process gets a ticket before another, or one gets interrupted and they both happen to get the same ticket number\\
In the case where one process gets a ticket before the other, then all other processes that came after will have to wait on that process to finish (i.e. the ticket = 0)\\
If they both have the same ticket number, then there is a tie breaking scenario and the process with the lesser ID will go.  This ensures that both will not go at the same time, and the other process will go once the first has set its ticket to 0\\
\newline
uncomment the code for part 1 in Simulation.java to see the results

\section*{Answer 2}
\begin{enumerate}
	\item This code works because ever processes is effectively waiting on every other process to arrive.  When one arrives, it signals, which means that anyone else waiting can then signal that process $i$ has arrived.  No process will be able to go until all proceeses are there, because the initial signal comes from process $i$.  Each semaphore should be initialized to 0\\

	\item No, because after the rendezvous, semaphore[i] will always be 1, therefore the code will not block.  The extra wait(semaphore[i]) is called to ensure that the semaphore goes back to 0

\section*{Answer 3}
\begin{enumerate}
	\item See code.  $R$ is an array the keeps track of priority for processes that are requesting the CS\\
	$N$ is the number of processes currently requesting the CS\\
	$B$ is an array of binary semaphores

	\item Uncomment 'Question3b' in Simulation.java to see output

	\item Uncomment 'Question3c' in Simulation.java

	\item Uncomment 'Question3d' in Simulation.java

	\item Starvation is possible in part A.  This is beause high priority requests will always beat low ones, so if there are a lot, low priority requests will not go.  In B and C, there is no possibility of starvation.  In part C, there is a bound of 0 out of order (because it is FIFO).  On part A there is no bound (because starvation is possible).
\end{enumerate}


\end{document} 